\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-15 paper.tex
Modifice el paper.tex y añadi la grafica celda1.png

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a which is an
electrically grounded good conductor. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/celdan1}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire with
    just the tip uncovered and located at $ \vec{r}_0 $ within the
    liquid.\notaL{\sout{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}}\notaL{\sout{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}}\notaL{\sout{Indica el voltaje y la
    corriente}}\notaL{\sout{¿Está bien la polaridad de la batería?}}}
    just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}\notaL{Indica el voltaje y la
    corriente}\notaL{Mejor pon una fuente de corriente en lugar de una
  fuente de voltaje}}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
and $\varphi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \varphi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current to the
electrode gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_0 = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\bm r_0=(x_0, y_0, z_0)$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

\subsection{GRIN Porous Silicon Microcavities}
 \begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Images/MicrGrin}
	\caption{Diagram of a microcavity of porous silicon
            GRIN. Alternate layers are obtained of high (H) refractive
            index $n_{Hi}$ and low (L) refractive index
            $n_{Li}$, where $N_H$ is the number of layers for
            $n_{Hi}$ and $N_L$ is the number of layers for
            $n_{Li}$. Then,  $d_{Hi}$ is the monolayer thickness
            of  $n_{Hi}$ at that measurement point and $d_{Li}$
            is the monolayer thickness of $n_{Hi}$ at that
            measurement point. Therefore,  $d_i$ is the total
            thickness calculated for each of the measurements,
            defining a i = $ A, B, C$. Having the following
            relationship $d_{_{i}} =
            (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) +
            (2d_{_{Hi}})$. }
            relationship $d_i =
            (N_{Hi}d_{Hi})+(N_{Li}d_{Li}) +
            (2d_{Hi})$. }}
	\label{fig:MCGRIN0}
\end{figure}
The Fig. \ref{fig:MCGRIN0} the scheme of  a initially proposed lateral
gradient for monolayers should be shown in section 4.2, where we
designed an electolytic cell suitable for our experiments and giving
us the expected results of the simulation in section 4.1. Now our
purpose is to manufacture more complex photonic structures such as the
Porous silicon microcavities GRIN, taking into account that we start
from having a tip electrode almost on the surface and by making a
variation of currents we can achieve the effect of alternating the
layers. Alternate layers are obtained of high (H) refractive index
$n_{Hi}$ and low (L) refractive index $n_{Li}$, where $N_{H}$
is the number of layers for  $n_{Hi}$ and $N_L$ is the number
of layers for $n_{Li}$. Then,  $d_{Hi}$ is the monolayer
thickness of  $n_{Hi}$ at that measurement point and $d_{Li}$ is
the monolayer thickness of $n_{Hi}$ at that measurement
point. Therefore,  $d_i$ is the total thickness calculated for
each of the measurements, defining a i = $ A, B, C$. Having the
following relationship $d_i =
(N_{Hi}d_{Hi})+(N_{Li}d_{Li}) + (2d_{Hi})$.
Initial data for conventional design we use  $\lambda_c= 0.67 \ \
\mu m$, $n_H =2.6$, $P_H =0.46$, $d_H=0.066 \ \ \mu m
$, $t_H=35 s  $ y para  $n_L= 1.4$,  $P_L =0.75$,
$d_L=0.117 \ \ \mu m  $, $t_L=11 s  $. All these data are
for the point $ 0 $ which is located at one end of the sample just
below the tip counter-electrode.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/MCGRIN2}
  \caption{a) Three locations at different points are
      considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B
      (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSMCGRIN
      sample $ GMC $. b) We have the reflectance measurements to
      know the optical properties with the proposed
      simulation. We were able to show that in a Porous Silicon
      GRIN structure, for a microcavity the data is very
      consistent with the simulation and the experiment, we
      found the refractive indices and the porosities as a
      function of the current density at each measurement point,
      see Table \ref{tabla:1}. }
  \label{fig:MCGRIN3}
\end{figure}

>>>>

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a which is an
electrically grounded good conductor. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/celdan1}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire with
    just the tip uncovered and located at $ \vec{r}_0 $ within the
    liquid.\notaL{\sout{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}}\notaL{\sout{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}}\notaL{\sout{Indica el voltaje y la
    corriente}}\notaL{\sout{¿Está bien la polaridad de la batería?}}
    just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}\notaL{Indica el voltaje y la
    corriente}\notaL{Mejor pon una fuente de corriente en lugar de una
  fuente de voltaje}}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
and $\varphi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \varphi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current to the
electrode gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_0 = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\bm r_0=(x_0, y_0, z_0)$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

\subsection{GRIN Porous Silicon Microcavities}
 \begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Images/MicrGrin}
	\caption{Diagram of a microcavity of porous silicon
            GRIN. Alternate layers are obtained of high (H) refractive
            index $n_{Hi}$ and low (L) refractive index
            $n_{Li}$, where $N_H$ is the number of layers for
            $n_{Hi}$ and $N_L$ is the number of layers for
            $n_{Li}$. Then,  $d_{Hi}$ is the monolayer thickness
            of  $n_{Hi}$ at that measurement point and $d_{Li}$
            is the monolayer thickness of $n_{Hi}$ at that
            measurement point. Therefore,  $d_i$ is the total
            thickness calculated for each of the measurements,
            defining a i = $ A, B, C$. Having the following
            relationship $d_i =(N_{Hi}d_{Hi})+(N_{Li}d_{Li}) +
            (2d_{Hi})$. }
	\label{fig:MCGRIN0}
\end{figure}
The Fig. \ref{fig:MCGRIN0} the scheme of  a initially proposed lateral
gradient for monolayers should be shown in section 4.2, where we
designed an electolytic cell suitable for our experiments and giving
us the expected results of the simulation in section 4.1. Now our
purpose is to manufacture more complex photonic structures such as the
Porous silicon microcavities GRIN, taking into account that we start
from having a tip electrode almost on the surface and by making a
variation of currents we can achieve the effect of alternating the
layers. Alternate layers are obtained of high (H) refractive index
$n_{Hi}$ and low (L) refractive index $n_{Li}$, where $N_{H}$
is the number of layers for  $n_{Hi}$ and $N_L$ is the number
of layers for $n_{Li}$. Then,  $d_{Hi}$ is the monolayer
thickness of  $n_{Hi}$ at that measurement point and $d_{Li}$ is
the monolayer thickness of $n_{Hi}$ at that measurement
point. Therefore,  $d_i$ is the total thickness calculated for
each of the measurements, defining a i = $ A, B, C$. Having the
following relationship $d_i =
(N_{Hi}d_{Hi})+(N_{Li}d_{Li}) + (2d_{Hi})$.
Initial data for conventional design we use  $\lambda_c= 0.67 \ \
\mu m$, $n_H =2.6$, $P_H =0.46$, $d_H=0.066 \ \ \mu m
$, $t_H=35 s  $ y para  $n_L= 1.4$,  $P_L =0.75$,
$d_L=0.117 \ \ \mu m  $, $t_L=11 s  $. All these data are
for the point $ 0 $ which is located at one end of the sample just
below the tip counter-electrode.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/MCGRIN2}
  \caption{a) Three locations at different points are
      considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B
      (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSMCGRIN
      sample $ GMC $. b) We have the reflectance measurements to
      know the optical properties with the proposed
      simulation. We were able to show that in a Porous Silicon
      GRIN structure, for a microcavity the data is very
      consistent with the simulation and the experiment, we
      found the refractive indices and the porosities as a
      function of the current density at each measurement point,
      see Table \ref{tabla:1}. }
  \label{fig:MCGRIN3}
\end{figure}
